---
title: "all"
author: "Tom Mushkat"
date: "2022-09-11"
output:
   html_document:
      code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE,message=FALSE}
pacman::p_load(tidyverse, doSPSS, here, ez, emmeans)

Data <- read_csv(here("Data//dataForAnalysis.csv"))
table(Data$Gender) / nrow(Data) * 100

ExpertDK <- c(1, 0, 0, 0)
ExpertKnow <- c(0, 1, 0, 0)
LaypersonDK <- c(0, 0, 1, 0)
LaypersonKnow <- c(0, 0, 0, 1)

ExpertDK <- c(1, 0, 0, 0)
ExpertKnow <- c(0, 1, 0, 0)
LaypersonDK <- c(0, 0, 1, 0)
LaypersonKnow <- c(0, 0, 0, 1)

dvCom_1 <- if_else(is.na(Data$Voltaren), Data$Wait, Data$Voltaren)
dvCom_2 <- if_else(is.na(Data$Physiotherapy), Data$Wait, Data$Physiotherapy)
dvCom_3 <- if_else(is.na(Data$CT), Data$Wait, Data$CT)
Data$Complaience <- rowMeans(cbind(Data$Physiotherapy, Data$CT))
Data$dvCom_4 <- sdOutliers(if_else(is.na(Data$Complaience), Data$Wait, Data$Complaience))
Data$dvCom_5 <- sdOutliers(if_else(is.na(Data$Voltaren), Data$Wait, Data$Voltaren))

Data <- Data %>%
  mutate(Condition = paste0(source_identity, source_answer
))

METI_Integrity <- Data %>% drop_na(METI_Benelovent)
METI_Benelovent <- Data %>% drop_na(METI_Benelovent)
comp <- Data %>%
  drop_na(dvCom_4)
fit1 = lm(METI_Expertise ~ Condition, data = Data)
fit2 = lm(METI_Integrity ~ Condition, data = METI_Integrity)
fit3 = lm(METI_Benelovent ~ Condition, data = METI_Benelovent)
fit4 = lm(dvCom_4 ~ Condition, data = comp)
```



# Expertise
## Descriptive_Statistics
```{r, warning=FALSE,message=FALSE}
modelTow <- twoWay(Data$METI_Expertise, Data$source_identity, Data$source_answer)
modelTow$Descriptive_Statistics
```

## ANOVA
```{r, warning=FALSE,message=FALSE}
e <- ezANOVA(data = Data, dv = METI_Expertise, wid = Q1, between = .(source_identity, source_answer), type = 3, return_aov = TRUE)
e$ANOVA
```
## Effect size partial Eta square
```{r, warning=FALSE,message=FALSE}
modelTow$Effect_zise
modelTow$Effect_interpretation
```

## Contrast ExpertDK - LaypersonDK
```{r, warning=FALSE,message=FALSE}

cont1 <- emmeans(fit1, specs = pairwise ~ Condition,
         at = list(Condition = c("ExpertDK", "LaypersonDK")))
cont1$contrasts
```

## Contrast ExpertKnow - LaypersonKnow

```{r, warning=FALSE,message=FALSE}

cont2 <- emmeans(fit1, specs = pairwise ~ Condition,
         at = list(Condition = c("ExpertKnow", "LaypersonKnow") ) )
cont2$contrasts
```

```{r, warning=FALSE,message=FALSE}


modelTow$Figure
```

# Integrity
## Descriptive_Statistics
```{r, warning=FALSE,message=FALSE}

modelTow <- twoWay(METI_Integrity$METI_Integrity, METI_Integrity$Expert, METI_Integrity$Ignorance)
modelTow$Descriptive_Statistics


```

## ANOVA
```{r, warning=FALSE,message=FALSE}
e <- ezANOVA(data = METI_Integrity, dv = METI_Integrity, wid = Q1, between = .(Expert, Ignorance), type = 3, white.adjust = TRUE, detailed = TRUE, return_aov = TRUE)
e$ANOVA
```
## Effect size partial Eta square
```{r, warning=FALSE,message=FALSE}
modelTow$Effect_zise
modelTow$Effect_interpretation
```

## Contrast ExpertDK - LaypersonDK
```{r, warning=FALSE,message=FALSE}

cont1 <- emmeans(fit2, specs = pairwise ~ Condition,
         at = list(Condition = c("ExpertDK", "LaypersonDK") ) )
cont1$contrasts
```

## Contrast ExpertKnow - LaypersonKnow

```{r, warning=FALSE,message=FALSE}

cont2 <- emmeans(fit2, specs = pairwise ~ Condition,
         at = list(Condition = c("ExpertKnow", "LaypersonKnow") ) )
cont2$contrasts
```
```{r, warning=FALSE,message=FALSE}


modelTow$Figure
```

# Benelovent
## Descriptive_Statistics
```{r, warning=FALSE,message=FALSE}

modelTow <- twoWay(METI_Benelovent$METI_Benelovent, METI_Benelovent$Expert, METI_Benelovent$Ignorance)
modelTow$Descriptive_Statistics
```

## ANOVA
```{r, warning=FALSE,message=FALSE}
e <- ezANOVA(data = METI_Benelovent, dv = METI_Benelovent, wid = Q1, between = .(Expert, Ignorance), type = 3, white.adjust = TRUE, detailed = TRUE, return_aov = TRUE)
e$ANOVA
```
## Effect size partial Eta square
```{r, warning=FALSE,message=FALSE}
modelTow$Effect_zise
modelTow$Effect_interpretation
```

## Contrast ExpertDK - LaypersonDK
```{r, warning=FALSE,message=FALSE}

cont1 <- emmeans(fit3, specs = pairwise ~ Condition,
         at = list(Condition = c("ExpertDK", "LaypersonDK") ) )
cont1$contrasts
```

## Contrast ExpertKnow - LaypersonKnow

```{r, warning=FALSE,message=FALSE}

cont2 <- emmeans(fit3, specs = pairwise ~ Condition,
         at = list(Condition = c("ExpertKnow", "LaypersonKnow") ) )
cont2$contrasts
```
```{r, warning=FALSE,message=FALSE}


modelTow$Figure
```

# Complaience
## Descriptive_Statistics
```{r, warning=FALSE,message=FALSE}

comp %>% 
  group_by(Expert) %>% 
  summarise(M = round(mean(dvCom_4), 2),
            SD = round(sd(dvCom_4), 2))

comp %>% 
  group_by(Ignorance) %>% 
  summarise(M = round(mean(dvCom_4), 2),
            SD = round(sd(dvCom_4), 2))

modelTow <- twoWay(comp$dvCom_4, comp$Expert, comp$Ignorance)
modelTow$Descriptive_Statistics
```

## ANOVA
```{r, warning=FALSE,message=FALSE}
e <- ezANOVA(data = comp, dv = dvCom_4, wid = Q1, between = .(Expert, Ignorance), type = 3, white.adjust = TRUE, detailed = TRUE, return_aov = TRUE)
e$ANOVA
```
## Effect size partial Eta square
```{r, warning=FALSE,message=FALSE}
modelTow$Effect_zise
modelTow$Effect_interpretation
```

## Contrast ExpertDK - LaypersonDK
```{r, warning=FALSE,message=FALSE}

cont1 <- emmeans(fit4, specs = pairwise ~ Condition,
         at = list(Condition = c("ExpertDK", "LaypersonDK") ) )
cont1$contrasts
```

## Contrast ExpertKnow - LaypersonKnow

```{r, warning=FALSE,message=FALSE}

cont2 <- emmeans(fit4, specs = pairwise ~ Condition,
         at = list(Condition = c("ExpertKnow", "LaypersonKnow") ) )
cont2$contrasts
```
```{r, warning=FALSE,message=FALSE}


modelTow$Figure
```